---
title: "datasauRus"
author: "Kasia Banas"
date: "2024-09-26"
output: html_document
---

Install and load the datasauRus library:

```{r}
# install.packages("datasauRus")
library(datasauRus)
```

Load the tidyverse: 
```{r}
library(tidyverse)
```

`datasaurus_dozen` is a dataset demonstrating the utility of visualization. 
These 12 datasets are equal in standard measures: mean, standard deviation, 
and Pearson's correlation. But they look very different
Run the chunk below to get more info about this dataset:

```{r}
?datasaurus_dozen
```

See what datasets are in the datasaurus_dozen:

```{r}
datasaurus_dozen %>% 
  distinct(dataset)
```

## Exercise 1
Pick 2 datasets and plot them next to one another
(I'd recommend scatterplot, use facets if you like)
```{r}

dino.star <- datasaurus_dozen %>% 
  filter(dataset == "dino" | dataset == "star")

dino.star %>% 
  ggplot(aes(x = x, y = y, colour = dataset)) +
  geom_point() +
  theme(legend.position = "left") +
  facet_wrap(~dataset, ncol = 3)

```

## Exercise 2
For these same two datasets, find the mean and standard deviation
for the x and y variable in each. What did you find? 

```{r}

dino <- datasaurus_dozen %>% 
  filter(dataset == "dino")

summary(dino)
sd(dino$x)
sd(dino$y)

star <- datasaurus_dozen %>%
  filter(dataset == "star")

summary(star)
sd(star$x)
sd(star$y)

```